Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Rework conclusion

\rev{We have found evidence of the flute instability using both models of
viscosity, however isotropic viscosity damps the initial growth such that it
does not develop beyond its linear phase before the faster growing kink
instability disrupts the flux tube and halts the development of the flute. Due
to the enhanced growth of the flute instability in the anisotropic case, the
tube becomes more readily mixed and the growth rate of the kink instability is
smaller. Beyond the effect on the growth of the two observed instabilities, the
two viscosity models greatly affect both the viscous heating and Ohmic heating
rates. Anisotropic viscosity is naturally less dissipative than isotropic
viscosity and generates approximately two orders of magnitude less total
viscous heat than isotropic viscosity. This is somewhat offset by the
anisotropic viscosity model permitting greater kinetic energy release and
enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
generation of small, strong current sheets. The overall effect is that more
heat is released when the viscosity is anisotropic. This is similarly observed
in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}

@@

\rev{The growth rate of the kink instability is, counter-intuitively, lower in
the weakly dissipative anisotropic cases, compared to the strongly dissipative
isotropic cases, i.e. one would expect the kink instability to grow more
quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
this behaviour, where the kink instability grows (marginally) faster in the
anisotropic cases. We conjecture it is the presence of the flute modes which
negatively affects the growth of the kink instability. It seems unlikely that
in the linear regime the perturbations of the flute and kink are able to
directly couple, given that the kink instability generally presents at the axis
of a flux tube and the flute at some resonant surface away from the axis.
Instead of a linear coupling, we believe that the linear kink instability is
affected by the more complex magnetic field configuration that arises due to
the mixing caused by the nonlinear development of the flute modes (for example,
compare figures~\ref{fig:field_line_plots_iso}
and~\ref{fig:field_line_plots_swi}).}

>>>>

\rev{We have found evidence of the flute instability using both models of
viscosity, however isotropic viscosity damps the initial growth such that it
does not develop beyond its linear phase before the faster growing kink
instability disrupts the flux tube and halts the development of the flute.
Given that most numerical studies of the kink instability employ isotropic or
shock viscosity, this is likely why the flute instability has not been
previously reported.

The growth rate of the kink instability is, counter-intuitively, lower in the
weakly dissipative anisotropic cases, compared to the strongly dissipative
isotropic cases, i.e. one would expect the kink instability to grow more
quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
this behaviour, where the kink instability grows (marginally) faster in the
anisotropic cases. We conjecture it is the presence of the flute modes which
negatively affects the growth of the kink instability. It seems unlikely that
in the linear regime the perturbations of the flute and kink are able to
directly couple, given that the kink instability generally presents at the axis
of a flux tube and the flute at some resonant surface away from the axis.
Instead of a linear coupling, we believe that the linear kink instability is
disturbed by the more complex magnetic field configuration that arises due to
the mixing caused by the nonlinear development of the flute modes. The
complexity in the field can be seen by comparing
figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}).

Beyond the effect on the growth of the two observed instabilities, the two
viscosity models greatly affect both the viscous heating and Ohmic heating
rates. Anisotropic viscosity is naturally less dissipative than isotropic
viscosity and generates approximately two orders of magnitude less total
viscous heat than isotropic viscosity. This is somewhat offset by anisotropic
viscosity permitting greater kinetic energy release and enhanced mixing, which
in turn enhances Ohmic dissipation of heat through the generation of small,
strong current sheets. The overall effect is that more heat is generated when
the viscosity is anisotropic, similar to what has been observed in previous
work~\citep{quinnEffectAnisotropicViscosity2020}. In the context of
coronal heating, this is encouraging: the use of a less dissipative viscosity
model actually results in greater overall heating. How this result generalises
to more realistic coronal resistivities, and whether this result holds true for
other coronal instabilities, should be the subject of further investigation.}

\rev{Since the flute instability only develops nonlinearly when using anisotropic viscosity, it is difficult to distinguish the effect of the instability from that of the viscosity itself on the viscous or Ohmic heating. TODO}

@@
